SVG: The Paper

### 2022-04-19 Analysis/index.Rmd
hexes

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))

>>>>

ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
  scale_fill_viridis_c() + scale_color_viridis_c() +
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),legend.position="none",
          panel.background=element_rect(color  = "#808080", size = 2,linetype = 'dotted', fill ="#808080"),
        panel.border= element_rect(colour = "black", fill=NA, size=5),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank()) -> plt_all

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y),
            .groups = "drop") %>%
  ggplot(aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c()+ scale_color_viridis_c() +
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),legend.position="none",
          panel.background=element_rect(color  = "#808080", size = 2,linetype = 'dotted', fill ="#808080"),
        panel.border= element_rect(colour = "black", fill=NA, size=5),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank()) -> plt_med

plt_all 
plt_med
